\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-05-03 paper_final.tex
Finished final part of hardest version. Still need Gabe to figure out what the number of examples needed for bounding is

\textbf{Theorem 2.}
\textit{ If $w_0$ is known and $ 0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ 
then $\mathbb{T}_{\epsilon}(w^*, \learn)  \leq 2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
}
\\
\\
\\
\textit{Proof.}
Assume WLOG $\lVert w^* \rVert = 1$.

Pick $(x_1,y_1)$ such that $y_1 = -1$, $\lVert x_1 \rVert = \frac{2 \lVert w_0 \rVert}{\epsilon \eta_{\min}}$ and $\langle x_1 , w^* \rangle = 0$.

@@

Then let $x_2 = \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2}w^* + x_1$.
It should be clear that then that $sign(\langle w* , x_2 \rangle) =  y_2 = 1$

@@

So
$$
y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
$$
$$
= \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
$$
$$
\leq \bigg( \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) \lVert w_0 \rVert - \eta \lVert x_1 \rVert^2
$$
$$
= \frac{2 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2} + \frac{2 \lVert w_0 \rVert ^2}{\epsilon \eta_{\min}} - \eta \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}^2}
$$
$$
\leq \frac{4 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2}  -  \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}}
$$
which is less than $0$ for $\epsilon < 1$, so $(x_2 , y_2)$ will cause the perceptron to update.

Then,
notice that $w_2 = w_0 +\eta \frac{2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} w^*$

Then 
$$
\frac{\langle w_2, w^* \rangle}{\lVert w_1 \rVert \lVert w^* \rVert} = \frac{
\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} \lVert w^* \lVert ^2 + \langle w_0, w^* \rangle}{\lVert w_2 \rVert}
$$ 
$$
\geq \frac{\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} - \lVert w_0 \rVert}{\lVert w_0 \rVert +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
$$
$$
= 1 - \frac{2 \lVert w_0  \rVert}{\lVert w_0 \rVert +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
$$
$$
= 1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{(\beta + \alpha)/2} } \epsilon
$$
$$
\geq  1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{\eta_{\max} - (\beta - \alpha) / 2} } \epsilon
$$
$$
\geq  1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{\eta_{\max} (1-\epsilon)} } \epsilon
$$
$$
\geq 1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{ 2  \lVert w_0 \rVert}{(1-\epsilon)} } \epsilon
$$
$$
\geq 1 - \epsilon
$$

@@

>>>>

\textbf{Theorem 2.}
\textit{ If $w_0$ is known , $w_0 \leq b < \infty$ and $ 0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ 
then $\mathbb{T}_{\epsilon}(w^*, \learn)  \leq 2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
}
\\
\\
\\
\textit{Proof.}
Assume WLOG $\lVert w^* \rVert = 1$.

Pick $(x_1,y_1)$ such that $y_1 = -1$, $\lVert x_1 \rVert = \frac{2 b}{\epsilon \eta_{\min}}$ and $\langle x_1 , w^* \rangle = 0$.

@@

Then let $x_2 = \frac{2 b}{\epsilon (\beta + \alpha)/2}w^* + x_1$.
It should be clear that then that $sign(\langle w* , x_2 \rangle) =  y_2 = 1$

@@

So
$$
y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 b}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
$$
$$
= \bigg\langle \frac{2 b}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
$$
$$
\leq \bigg( \frac{2 b}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) b - \eta \lVert x_1 \rVert^2
$$
$$
\leq \frac{4 b ^2}{\epsilon \eta_{\min}} - \eta \frac{4 b^2}{\epsilon^2 \eta_{\min}^2}
$$
$$
\leq \frac{4 b^2}{\epsilon \eta_{\min}}  -  \frac{4 b^2}{\epsilon^2 \eta_{\min}}
$$
which is less than $0$ for $\epsilon < 1$, so $(x_2 , y_2)$ will cause the perceptron to update.

Then,
notice that $w_2 = w_0 +\eta \frac{2  b}{\epsilon (\beta + \alpha)/2} w^*$

Then 
$$
\frac{\langle w_2, w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} = \frac{
\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} \lVert w^* \lVert ^2 + \langle w_0, w^* \rangle}{\lVert w_2 \rVert}
$$ 
$$
\geq \frac{\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} - b}{b +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
$$
$$
= 1 - \frac{2 b}{b +\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} }
$$
$$
= 1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{(\beta + \alpha)/2} } \epsilon
$$
$$
\geq  1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{\eta_{\max} - (\beta - \alpha) / 2} } \epsilon
$$
$$
\geq  1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{\eta_{\max} (1-\epsilon)} } \epsilon
$$
$$
\geq 1 - \frac{2b}{b \epsilon + \frac{ 2  b}{(1-\epsilon)} } \epsilon
$$
$$
\geq 1 - \epsilon
$$

@@

\textbf{Theorem 4.} 
\textit{With unknown $w_0$ such that $\lVert w_0 \rVert \leq b < \infty$
and unknown $\eta$ such that $0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ then 
$
\mathbb{T}_\epsilon(w^* , \learn) \leq 3 + ?
$
}
\\
\\
\\
\textit{Proof.}
First using \textbf{Algorithm 3} bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$

Then WLOG assume $\lVert w^8 \rVert = 1$. Then pick an $x_1$ such that 
$\lVert x_1 \rVert = \frac{2b}{\epsilon (\beta + \alpha)/2}$ and $\langle w^*, x_1 \rangle = 0$. Such an $x_1$ always exists. Then, let $x'_1 = -x_1.$ Then $y_1 = y'_1 = \text{sign}(\langle w*, x_1 \rangle) = -1$.  Then since $y_1 = y'_1$ then the perceptron must make an error on one of the examples. So first give $(x_1, y_1)$ to the perceptron.
\underline{Case 1}: If $(x_1, y_1)$ then $w_1 = w_0 - \eta x_1$. 
Then select at the second iteration an $x_2 = \frac{2b}{\epsilon (\beta + \alpha)/2}$. Using the same logic from theorem 2, we can see that this will give us our desired $\epsilon$ approximate $w_2$.

\underline{Case 2}: If $(x_1, y_1)$ did not cause and update then set $x_2 = x'_1$ , $y_2 = y'_1$ and $x_3 = \frac{2b}{\epsilon (\beta + \alpha)/2}w^* + x_2$. Using very similar logic to how Case 1 used Theorem 2, we can see that this will also get us the desired $\epsilon$ approximate $w_3$.

In Case 1 we require 2 examples and and Case 2 we require 3, so including the examples needed to bound $\eta$ we get that 
$$
\mathbb{T}_\epsilon(w^*, \learn) \leq 3 + ?
$$
